Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-09-17 drafts/draft.tex
unremarkable progress commit

%\chapter{Introduction}
%
%TODO

@@

% - 
%
%
%
%
%

@@

Researchers have shown that vegetation stem dimensions, spatial density, and Reynolds number are important predictors of sediment transport and deposition behavior in flow through vegetated regions, particularly because of the dual effect of vegetation on increasing turbulence and drag \citep{Fauria_2015, nepf_drag_1999, Palmer_2004}. Thus, flow intensity has considerable significance in this context because its interaction with vegetation elements affect flow conditions, which in turn affect the ability of flow to entrain sediment. Sediment capture in creeping flow can be derived analytically (look up references), and many experiments have been done at the limits of laminar and fully turbulent flows to characterize sediment capture with vegetation \citep{Shan_turbulence_2020, Wu_2011, Yang_2016}. However, experiments at transitional flows are more sparse \citep{Fauria_2015, Palmer_2004, Purich_2007}. These types of flows have real-world importance because they can be typical of shallow, low-sloping wetland environments where dense vegetation cover makes vegetation-flow interactions common. Existing predictive models of sediment capture in transitional flows generally do not agree well with each other, and do not separate effects of direct capture on vegetation versus gravitational settling \citep{Fauria_2015, Palmer_2004}. In this study, we follow the strategy of previous work by using laboratory flume experiments to quantify sediment capture in vegetated reaches but build on existing studies of transitional flows by partitioning sediment capture into contributions by vegetation and gravitational settling for multiple vegetation densities and flow velocities

>>>>

@@

@@

Researchers have shown that vegetation stem dimensions, spatial density, and Reynolds number are important predictors of sediment transport and deposition behavior in flow through vegetated regions, particularly because of the dual effect of vegetation on increasing turbulence and drag \citep{Fauria_2015, nepf_drag_1999, Palmer_2004}. Thus, flow intensity has considerable significance in this context because its interaction with vegetation elements affects flow conditions, which in turn affect the ability of flow to entrain sediment. Sediment capture in creeping flow can be derived analytically (look up references), and many experiments have been done at the limits of laminar and fully turbulent flows to characterize sediment capture with vegetation \citep{Shan_turbulence_2020, Wu_2011, Yang_2016}. However, experiments at transitional flows are more sparse \citep{Fauria_2015, Palmer_2004, Purich_2007}. These types of flows have real-world importance because they can be typical of shallow, low-sloping wetland environments where dense vegetation cover makes vegetation-flow interactions common. Existing predictive models of sediment capture in transitional flows generally do not agree well with each other, and do not separate effects of direct capture on vegetation versus gravitational settling \citep{Fauria_2015, Palmer_2004}. In this study, we follow the strategy of previous work by using laboratory flume experiments to quantify sediment capture in vegetated reaches but build on existing studies of transitional flows by partitioning sediment capture into contributions by vegetation and gravitational settling for multiple vegetation densities and flow velocities
